Meesters TODO List

### 2023-03-21 files/Chapter2/generalvibrationmodel.tex
notes on discussion

@@

@@

@@

\subsection{General vibration problem}

\textcolor{red}{CVV18 moet in die subsection verwys word.}\\

@@

\textcolor{red}{Following the method of seperation of variables,} $u(t) = T(t)x$ is a solution of the homogeneous problem
\begin{eqnarray}
	c(u''(t),v) + b(u(t),v) = 0
\end{eqnarray}
if and only if
\begin{eqnarray}
	T''  + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

@@

\subsubsection{Comparison of models}
In a later chapter of this dissertation, different dimensional models are compared with each other. Since the formal series solution is a linear combination of eigenvalues and eigenfunctions, it is only required to compare the eigenvalues and eigenfunctions of the different models.\\

>>>>

Kan sien met substituting, meer

MODAL solution\\

@@

As w en phi kan 2.4.1 en () dan sal .... nie nodig nie. Probeer so ver as moontlik nie seperation of variables gebruik nie. Se eerder oof w en phi is sin en cos\\

@@

Los voorlopig hier.\\

@@

\subsection{General vibration problem new}
\subsection{General vibration problem old}

\textcolor{red}{CVV18 word verwys, kyk onder}\\

@@

nie seperation of variables nie, eers question dan cvv. Kry modal solutions, kan ons dit nou gebruik om algemene solution te kry?
\textcolor{red}{Following the method of seperation of variables,} $u(t) = T(t)x$ is a solution of the homogeneous problem
\begin{eqnarray}
	c(u''(t),v) + b(u(t),v) = 0
\end{eqnarray}
if and only if
\begin{eqnarray}
	T''  + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

@@

\subsubsection{Comparison of models}
Hele disseratoin gaan oor comparison of models. \\

In a later chapter of this dissertation, different dimensional models are compared with each other. Since the formal series solution is a linear combination of eigenvalues and eigenfunctions, it is only required to compare the eigenvalues and eigenfunctions of the different models.\\
